Evaluating a lightweight transcriptome assembly pipeline on two closely related ascidian species

### 2014-09-15 manuscript/main.tex
update figures

\documentclass[fleqn,10pt]{wlpeerj}
\title{Assembly on Cloud 9: Assembly metric assessment using Transcriptomes of closely related Ascidian species}

\author[1]{Elijah K. Lowe}
\author[2]{Billie J. Swalla}
\author[3]{C. Titus Brown}
\affil[1]{Michigan State University, Computer Science and Quantitative Biology, East Lansing, Michigan, 48824, USA}
\affil[2]{University of Washington, Biology Department and Friday Harbor Laboratories, Seattle, Washington, 98195, USA}
\affil[3]{Michigan State University, Microbiology and Molecular Genetics, and Computer Science and Engineering, East Lansing, Michigan, 48824, USA}

@@

Next generation sequencing (NGS) has allowed us to study organisms with a broader lens, looking at entire genomes and transcriptomes instead of single genes.  This capability is particularly important for non-model organisms where little prior knowledge may be available, and where NGS readily enables whole-transcriptome analyses \citep{wang_rna-seq:_2009}, allowing the study of organisms that are ecologically or evolutionarily interesting.

>>>>

\documentclass[fleqn,10pt]{wlpeerj}
\title{Evaluating a lightweight transcriptome assembly pipeline on two closely related ascidian species}

\author[1,2]{Elijah K. Lowe}
\author[3]{Billie J. Swalla}
\author[4,2,1]{C. Titus Brown}
\affil[1]{Michigan State University, Computer Science and Engineering,East Lansing, Michigan, 48823, USA}
\affil[2]{Michigan State University, Quantitative Biology, East Lansing, Michigan, 48823, USA}
\affil[3]{University of Washington, Biology Department and Friday Harbor Laboratories, Seattle, Washington, 98195, USA}
\affil[4]{Michigan State University, Molecular Genetics, East Lansing, Michigan, 48823, USA}

@@

Next generation sequencing (NGS) has allowed us to study organisms with a broader lens, looking at entire genomes and transcriptomes instead of single genes.  This capability is particularly important for non-model organisms where little prior knowledge may be available, and where NGS readily enables whole-transcriptome analyses \citep{wang_rna-seq:_2009}, allowing us to study organisms that are ecologically or evolutionarily interesting, amongst other biological applications.
